The problem and promise of scale in multilayer networks

### 2019-09-27 paper/table1.Rmd
use table format md, works in pdf, word, gh doc

---
output: 
#   pdf_document
# classoption: landscape
  # word_document:
  #   reference_docx: template.docx
  github_document
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "-- `r Sys.Date()`"
---

@@

knitr::kable(tab1[c(1:7, 9)])
```

>>>>

---
output: 
  # pdf_document
# classoption: landscape
  word_document:
    reference_docx: template.docx
  # github_document
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "`r Sys.Date()`"
---

@@

knitr::kable(tab1)
```
